Computer Science House Constitution

### 2023-10-31 constitution.tex
Update #44 Review Responsibilities of the Research and Development Director (#64)
* Update 5.C.7 per Discussion

* Readd and reword point (d) of 5.C.7

* Remove period at end of point (d)
Removed last line (#114)
Add quorum requirement for Maintainer nominations (#99)

\asection{Constitution}
The House Constitution is written and maintained by the House and defines the major aspects, goals, and governing structure of the house.
It is reviewed annually by the Department of Residence Life.

@@

\asubsection{Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration.
The Executive Board may choose to approve or reject the nomination by Simple Majority vote.

@@

\asubsection{Responsibilities of the Research and Development Director(s)}
\begin{enumerate}
	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
	\item To exercise general supervision over Research and Development operations
	\item To oversee the planning, organization and construction of technical projects for the House's benefit
	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
	\item To provide seminars and tutorials to educate House members in technical areas
	\item To vote on issues presented to the Executive Board
\end{enumerate}

>>>>

\asection{Constitution}
The House Constitution is written and maintained by the House and defines the major aspects, goals, and governing structure of the house.

@@

\asubsection{Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration.
The Executive Board may choose to approve or reject the nomination by Simple Majority vote with a quorum of seventy-five percent of the Total Number of Possible Votes.

@@

\asubsection{Responsibilities of the Research and Development Director(s)}
\begin{enumerate}
	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
	\item To exercise general supervision over Research and Development operations
	\item To oversee the planning, organization and construction of technical projects for the House's benefit
	\item To strive to fulfill the House's need for technical equipment
	\item To provide seminars and tutorials to educate House members in technical areas
	\item To vote on issues presented to the Executive Board
\end{enumerate}
